### 2013-07-09 latex/paper-PLOS_ONE-revised.tex
Fixing figure caption.
Final last touches to the paper.

In many applications, specifically in the context of sequence evolution, RSA is treated as a site-specific property that is invariant under mutation. While RSA values of homologous structures tend to be strongly correlated \cite{RostSander1994,Zhouetal2009}, individual sites, in particular exposed ones, can show substantial RSA variability \cite{RostSander1994}. In this context, it is important to note that one potential source of RSA variability in previous studies was RSA normalization. For example, Ref.~\cite{RostSander1994} used the Rose scale, which differs quite substantially from the scale we propose here. In particular, the corrections we propose to the Rose scale range from 3\% (for His) to 18\% (for Asp), and are approximately uniformly distributed in that range over the 20 amino acids. Thus, many scenarios are possible under which a substitution might not change RSA under our scale but might change it up to 15\% under the Rose scale. A detailed analysis of RSA variability among homologous structures is beyond the scope of this work, but should be undertaken in future work.

@@

\begin{figure}[H]
\includegraphics[width=3in]{figures/Figure2.pdf}
\caption{\label{fig:RamaAla}Ramachandran plot for alanine residues in our empirical data set. Coordinates which correspond to RSA values $>1$ are shown in black and are clearly concentrated around coordinates $(-50^\circ,-45^\circ)$. We therefore propose that this region contains the maximally exposed conformation of alanine and should be used for calculating maximum SA.}
\end{figure}

>>>>

In many applications, specifically in the context of sequence evolution, RSA is treated as a site-specific property that is invariant under mutation. While RSA values of homologous structures tend to be strongly correlated \cite{RostSander1994,Zhouetal2009}, individual sites, in particular exposed ones, can show substantial RSA variability \cite{RostSander1994}. In this context, it is important to note that one potential source of RSA variability in previous studies was RSA normalization. For example, Ref.~\cite{RostSander1994} used the Rose scale, which differs quite substantially from the scale we propose here. In particular, the corrections we propose to the Rose scale range from 4\% (for Leu) to 18\% (for Asp), and are approximately uniformly distributed in that range over the 20 amino acids. Thus, many scenarios are possible under which a substitution that might not change RSA under our scale might change it by over 10\% under the Rose scale. A detailed analysis of RSA variability among homologous structures is beyond the scope of this work, but should be undertaken in future work.

@@

\begin{figure}[H]
\includegraphics[width=3in]{figures/Figure2.pdf}
\caption{\label{fig:RamaAla}Ramachandran plot for alanine residues in our empirical data set. Coordinates which correspond to RSA values $>1$ are shown in red and are clearly concentrated around coordinates $(-50^\circ,-45^\circ)$. We therefore propose that this region contains the maximally exposed conformation of alanine and should be used for calculating maximum SA.}
\end{figure}
